Checkpoint 3

### 2020-04-23 Checkpoint3.Rmd
fed's graph
keep the range

>>>>

```{r}
google_ts<-read.csv("Time_series_Google.csv")

day1<-as.Date("03/10/2020",format = "%m/%d/%Y")
day2<-as.Date("03/24/2020",format = "%m/%d/%Y")

google_ts_reg<-google_ts_reg%>%
  mutate(Day = as.Date(as.character(Day)))

a<-google_ts_reg %>% 
  #filter(Day<=day2)%>%
  #filter(Day>=day1)%>%
  group_by(Region, Day) %>% 
  summarize(ChinaVirusSearch = median(ChinaVirusInterest)) %>% 
  ggplot(aes(x=Day, y=ChinaVirusSearch, color=Region))+
  geom_point()

ggplotly(a)
```
